Towards a miniKanren with fair search strategies

### 2019-05-22 Paper/paper.tex
Changed a NOTE.

@@

\NOTE[DPF]{When we talk about complete and incomplete, I think we should
make it explicit that we are only talking about (run n (x y z) g ...) and
not (run* (x y z) g ...), but an alternative could be something like is
a stream that is always growing.  There is a term for this, likes makes
progress, but my mind is hiding the word from me.  It will come to me, but
not at this moment.}

>>>>

\NOTE[DPF]{We should reference the earliest paper (See Will Byrd vita)

@@

\NOTE[DPF]{When we talk about complete and incomplete, I think we should
make it explicit that we are only talking about (run n (x y z) g ...) and
not (run* (x y z) g ...), but an alternative is that a stream is \emph{productive}
or \emph{unproductive}.}
